Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization

### 2021-11-30 rCode/Draft.Rmd

@@

>>>>

We find that, in aggregate, manufacturing job losses were a driver of change in Democratic vote share in the 2016 election. Breaking it down by race, we see that [TO DO: complete thought]. Using our main results from regression 3 in Table 4, we simulate a counterfactual scenario to demonstrate the practical signifcance of our estimates. Specifically, we generate a counterfactual democratic vote share assuming that all counties experienced manufacturing job losses equivalent to the county at the 25th national percentile. In Figure 3, we show the difference between the counterfactual democratic vote share and the model-predicted democratic vote share. We highlight states in purple if the difference between the counterfactual and model-predicted democratic vote shares exceeded Trump's vote share margin. Figure 3 shows that the effect sizes from our analysis suggest that, but for manufacturing layoffs from 2004-2015, Trump may not have one the 2016 presidential election.

Additionally, we find that, given the evolution of the business cycle, considering only recent job losses can paint a misleading picture of the relationship between manufacturing job losses and changes in vote share. In fact, we find that net manufacturing job losses from 2004 to 2011 are crucial to explaining Trump's 2016 win. This finding suggests that economic changes, like manufacturing layoffs, can have lagged and variable political consequence.

@@

### 1. Figure 1: Manufacturing Layoffs Over Time
